I would like to declare my deep gratitude to all my mentors, colleagues, and collaborators who have supported my thesis project. My most prominent thank would go to Dr. Aurelio Teleman for giving me the great opportunity to work with him on this fascinating topic regarding the metabolism control related to diabetes. He has been always supportive and keeping on bringing in inspiration and insight to my PhD study. Special thanks also go to Cristina Pallares Cartes, Xiaojun Xu, Tiebe Marcel, Katrin Stra{\ss}burger, Sibylle Schleich, and other past and current members in Dr. Aurelio Teleman's Lab, for generous sharing their in-depth knowledge and intensive discussion at every step of the study. Huge thanks also go to Katharina Schindler in Dr. Aurelio Teleman's Lab for generous helping in preparing German version of the thesis abstract. I would also thank them for building a nice working atmosphere in the lab, and making it a pleasure and good memory to work with them. 

I am remarkably grateful to my joint collaborators Prof. Stephan Herzig and Dr. Mauricio Berriel Diaz for generous providing resources in the animal study, kind disscussions and suggestions throughout the study. Also special thanks to Oksana Seibert, Anja Reimann, Daniela Strzoda, Annika Zota, Tjeerd Sijmonsma, Roldan De Guia in Prof. Herzig's Lab for warmhearted help in performing animal study and virus production. I would also thank my collaborators Prof. Matthias Bl\"uher and Dr. Joan J Vendrell for sharing their cohort study results to extend my study to diabetes. I would also like to give my special thanks to the DKFZ Geonomics and Proteomics core facility for performing high-throughput experiments for my project. I want to thank Prof. Herbert Steinbei{\ss}er for his invaluable suggestions as my TAC member -- too unfortunate he can not see me graduate.

I thank Dr. Aurelio Teleman and Prof. Boutros for reading and evaluating my thesis.

In the end, I want to deeply thank my wife, Xueping Wu, my parents, Lixin Cheng and Taoying Wang, my sisters, Xiaoyun Cheng and Haiyun Cheng for continuous self-sacrificing supports during my PhD study in Germany. 


%I would also express my gratitude to Katrin Stra{\ss}burger for starting the great story with PP2A in \textit{Drosophilla}, which drives my study in mammalian system.